Pillar 1 - Sequential Pattern Mining

### 2019-02-19 Pillar 1 - Sequential Pattern Mining.Rmd
constrains on sequence rules "not take => low" and "not take => fail"

  # lhs not, rhs low
  filter(
    str_detect(rhs, "fail")
    )
```

@@

  # lhs not, rhs low
  filter(
    str_detect(rhs, "low")
    )
```

@@

```{r save rules, include = FALSE}
save(
  AR, SR,
  file = "App/rules/rules.RDATA"
  )
```

>>>>

  # lhs not, rhs low
  filter(
    str_detect(rhs, "fail"),
    lift > 1,
    confidence >= 0.40
    )
```

@@

  # constraints to respect
  filter(
    str_detect(rhs, "low"),
    lift > 1,
    confidence >= 0.40
    )
```

@@

```{r save rules, include = FALSE}
save(
  AR, SR,
  file = "App/rules/rules.RDATA"
  )

save(
  AR, SR,
  file = "App/Recommender System/rules.RDATA"
  )
```
